The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-09-06 analysis/paper/paper.qmd

emu_documents |> 
  inner_join(emu |> 
               select(ID, graduation_year), 
             by = c("document" = "ID")) |> 
  ggplot(aes(x = reorder(str_sub(document, 1, 50), gamma), y = gamma, fill = topic)) + 
  geom_bar(stat = "identity") + 
  coord_flip() + 
  facet_wrap(~ graduation_year, ncol = 1, scales = "free", drop = TRUE)

>>>>

emu_documents |>
  mutate(document = as.numeric(document)) |> 
  inner_join(emu |> 
               select(ID, graduation_year), 
             by = c("document" = "ID")) |> 
  ggplot(aes(x = reorder(str_sub(document, 1, 50), gamma), y = gamma, fill = topic)) + 
  geom_bar(stat = "identity") + 
  coord_flip() + 
  facet_wrap(~ graduation_year, ncol = 1, scales = "free", drop = TRUE)
